Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-31 Arxiv/main.tex
Update Arxiv/main.tex
update codes for experiments and fix typos in proof
update typos

\section{Mechanism Proposition}
\label{sec_mechs}
Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
\[
  \candidateset{\dataobs}\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
\]
where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
Notice that $\candidateset{\dataobs}$ has $n + 1$ elements, and
the Bayesian Inference process will produce an element from $\candidateset{\dataobs}$
that we denote by $\bysinfer(\dataobs)$ -- we don't explicitly
parametrize the result by the prior, which from now on we consider
fixed and we denote it by $\bprior$.

@@

\subsubsection{Exponential Mechanism}
Exponential mechanism $\expmech{}{x}{u}{\candidateset{\dataobs}}$ samples a element from the candidate set $\candidateset{\dataobs} = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
\begin{equation*}
\underset{z \thicksim \expmech{}{x}{u}{\candidateset{\dataobs}} }{Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
\end{equation*}
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity calculated by:
\begin{equation*}
GS = 
\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

@@

\subsubsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset{\dataobs}}$ share the same candidate set and utility function as it with standard exponential mechanism. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
\begin{equation*}
\underset{z \thicksim \expmech{local}{x}{u}{\candidateset{\dataobs}}}{\Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
\end{equation*}

@@

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset{\dataobs}$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\nomalizer{\dataobs}}.
\end{equation*}
where $S_\beta(\dataobs)$ is the smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:

\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\bigg\},
\end{equation}
where $d$ is the Hamming distance between two datasets, and $\beta =
\beta(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$. 
\end{definition}

This mechanism is based on the basic exponential mechanism
\cite{talwar}, with $\candidateset{\dataobs}$ as the range and
$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
that in this mechanism we don't calibrate the noise w.r.t. to the
global sensitivity of the scoring function but w.r.t. to the smooth
sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
$\hellinger(\bysinfer(\dataobs), \cdot)$.

@@

This mechanism also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
\]
and by replacing the $\candidateset{\dataobs}$ with set of posterior Dirichlet
distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range
over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
that $\candidateset{\dataobs}$ has $\binom{n + 1}{m - 1}$ elements in this case. We
will denote by $\hexpmechd$ the mechanism for the
Dirichlet-multinomial system.

@@

In what follows, let $ \ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset{\dataobs}$, we first introduce Lemma \ref{lem_score_pro_eq} and \ref{lem_score_pro_convert}.

\begin{lem}
\label{lem_score_pro_eq}
  Given $\hexpmech(\dataobs)$ and arbitrary $r_1, r_2 \in \candidateset{\dataobs}$, then following holds:
  $$
  \ux{r_1} = \ux{r_2} \iff \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}.
  $$  
\end{lem}
\begin{proof} of Lemma \ref{lem_score_pro_eq}.
\begin{itemize}
  \item $\implies$

@@

  Apply $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset{\dataobs}$:\\
  $\implies \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2)$. \\
  $\implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}$.

@@

  Apply\ $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset{\dataobs}$:
  $\implies \ux{r_1} = \ux{r_2}$.

@@

  Given $\hexpmech(\dataobs)$, define $R^{\dataobs}_r \subset \candidateset{\dataobs}$, s.t. $r' \in R^{\dataobs}_r \iff \ux{r'} = \ux{r}$.

@@

\begin{lem}
\label{lem_score_pro_convert}
 Given $\hexpmech(\dataobs)$, then the following property holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}
 \end{equation*}
\end{lem}
\begin{proof} of Lemma \ref{lem_score_pro_convert}.\\
To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
$\iff $ to compute $\hexpmechPr{\dataobs}{ z \in R | R = \{r' | r' \in \candidateset{\dataobs} \land \ux{r'} = \ux{r}\}}.$\\
By Definition \ref{def_cardinality}, $R^{\dataobs}_r$ is this set.\\
$\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{z \in R^{\dataobs}_r} $.\\
By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R^{\dataobs}_r}  =\sum\limits_{r'\in R^{\dataobs}_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
Apply Lemma \ref{lem_score_pro_eq} in $R^{\dataobs}_r$, \\
$\implies$ for any $r', r''\in R^{\dataobs}_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
$\implies$ $\sum\limits_{r'\in R^{\dataobs}_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
$\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
\end{proof}

@@

Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. In Beta-binomial system, for any $r\in \candidateset{\dataobs}$, let $\epsilon\geq 0$ and $\ux{r} + k \geq 0$, the following \emph{sliding property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}.
\end{equation*}
\end{lem}

@@

\todo{
In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$. Let $\mathcal{R}_1$, $\mathcal{R}_2$ be a partition of $\candidateset{\dataobs}$:
\begin{itemize}
  \item[*] $\mathcal{R}_1 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{\dataobs}{r} = 1\}$.
  \item[*] $\mathcal{R}_2 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{\dataobs}{r} = 2\}$.
\end{itemize}
}

@@

\noindent \textbf{Dilation Property of $\hexpmech$}
\begin{lem}
\label{lem_dilation}
Given $\hexpmech(\dataobs)$ in Beta-binomial system, for any $r\in \candidateset{\dataobs}$, let $\lambda < |\gamma|$, $\epsilon$, $|\delta'| < 1$ and $\gamma \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset{\dataobs}|})})$, the following \emph{dilation property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
\end{equation*}
\end{lem}

@@

  \begin{assert}
  \label{cardinality_eq}
  For any $r\in \candidateset{\dataobs}$, $\cardinality{\dataobs}{r} = \cardinality{\dataobs}{t}$.
  \end{assert}

@@

          Based on the accuracy property of exponential mechanism:
          \begin{equation*}
          \begin{split}
          Pr[u(\expmech{}{x}{u}{\candidateset{\dataobs}}) \leq c] 
          & \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},\\
          \end{split}
          \end{equation*}
          we derived the accuracy bound for $\hexpmech$:
          \begin{equation*}
          Pr[u(\hexpmech(\dataobs), \dataobs) \leq c] \leq |\candidateset{\dataobs}|exp(\frac{\epsilon c}{2 S(\dataobs)}).
          \end{equation*}

          apply this bound to Equation. \ref{eq_dilation_case2}:
          \begin{equation*}
          \begin{split}
          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
          & = |\candidateset{\dataobs}|exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
          & = |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
          \end{split}
          \end{equation*}

          By setting $|\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}) = 1 - \frac{\delta'}{2}$, 
          \begin{equation*}
          \begin{split}
          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] = 1 - \frac{\delta'}{2}
          \end{split}
          \end{equation*}
          holds, i.e.,
          \begin{equation*}
          \ux{r}
          \leq 
          \frac{S(\dataobs)}{(1 - e ^ {\lambda})},
          \end{equation*}         
          holds with failure probability $\frac{\delta'}{2}$ is proved.

          Particularly, $|\candidateset{\dataobs}| = n + 1$ because in Beta-binomial system.

@@

      Apply Lemma \ref{lem_dilation}:
      \begin{equation*}
      \begin{split}
      & \leq \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \hexpmechPr{\dataobs}{\ux{z} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r} } \\
      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big).
      \end{split}
      \end{equation*}

      Let $\ux{t} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r}$:      
      \begin{equation*}
      \begin{split}
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \hexpmechPr{\dataobs}{\ux{z} = \ux{t} } \\
      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big).
      \end{split}
      \end{equation*}

      Apply Lemma \ref{lem_score_pro_convert}:
      \begin{equation*}
      \begin{split}
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t } \\
      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big).
      \end{split}
      \end{equation*}

      Apply Definition \ref{def_smoo} and $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset{\dataobs}$:
      \begin{equation*}
      \begin{split}          
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \cardinality{\dataobs}{t}  \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big).
      \end{split}
      \end{equation*}

      Apply $\ux{t} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r}$ and simplify:\\
      \begin{equation*}
      \begin{split}          
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \cardinality{\dataobs}{t} \frac{exp(\frac{-\epsilon (\uxadj{r})}{2 S(\dataobs')})}{\unomalizer{\dataobs'}}\\
      & + 1 - |\candidateset{\dataobs}|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big).
       \end{split}
      \end{equation*}

>>>>

\section{Mechanism Proposition}
\label{sec_mechs}
Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
\[
  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
\]
where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
Notice that $\candidateset$ has $n + 1$ elements, and
the Bayesian Inference process will produce an element from $\candidateset$
that we denote by $\bysinfer(\dataobs)$ -- we don't explicitly
parametrize the result by the prior, which from now on we consider
fixed and we denote it by $\bprior$.

@@

\subsubsection{Exponential Mechanism}
Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
\begin{equation*}
\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
\end{equation*}
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity calculated by:
\begin{equation*}
GS = 
\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

@@

\subsubsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with standard exponential mechanism. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
\begin{equation*}
\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
\end{equation*}

@@

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\nomalizer{\dataobs}}.
\end{equation*}
where $S_\beta(\dataobs)$ is the smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:

\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\bigg\},
\end{equation}
where $d$ is the Hamming distance between two datasets, and $\gamma$ is the smooth upper bound in smooth sensitivity.
\end{definition}

This mechanism is based on the basic exponential mechanism
\cite{talwar}, with $\candidateset$ as the range and
$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
that in this mechanism we don't calibrate the noise w.r.t. to the
global sensitivity of the scoring function but w.r.t. to the smooth
sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
$\hellinger(\bysinfer(\dataobs), \cdot)$.

@@

This mechanism also extends to the Dirichlet-multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\sqrt{\betaf(\valpha_1) \betaf(\valpha_2)}}},
\]
and by replacing the $\candidateset$ with set of posterior Dirichlet
distributions candidates. Also, the smooth sensitivity $S(\dataobs)$
in (\ref{eq:smooth}) will be computed by letting $\dataobs'$ range
over all the elements in $\datauni^{n}$ adjacent to $\dataobs$. Notice
that $\candidateset$ has $\binom{n + 1}{m - 1}$ elements in this case. We
will denote by $\hexpmechd$ the mechanism for the
Dirichlet-multinomial system.

@@

In what follows, let $ \ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$, we first introduce Lemma \ref{lem_score_pro_eq} and \ref{lem_score_pro_convert}.

\begin{lem}
\label{lem_score_pro_eq}
  Given $\hexpmech(\dataobs)$ and arbitrary $r_1, r_2 \in \candidateset$, then following holds:
  $$
  \ux{r_1} = \ux{r_2} \iff \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}.
  $$  
\end{lem}
\begin{proof} of Lemma \ref{lem_score_pro_eq}.
\begin{itemize}
  \item $\implies$

@@

  Apply $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$:\\
  $\implies \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2)$. \\
  $\implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}$.

@@

  Apply\ $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$:
  $\implies \ux{r_1} = \ux{r_2}$.

@@

  Given $\hexpmech(\dataobs)$, define $R^{\dataobs}_r \subset \candidateset$, s.t. $r' \in R^{\dataobs}_r \iff \ux{r'} = \ux{r}$.

@@

\begin{lem}
\label{lem_score_pro_convert}
 Given $\hexpmech(\dataobs)$, then the following property holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}
 \end{equation*}
\end{lem}
\begin{proof} of Lemma \ref{lem_score_pro_convert}.\\
To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
$\iff $ to compute $\hexpmechPr{\dataobs}{ z \in R | R = \{r' | r' \in \candidateset \land \ux{r'} = \ux{r}\}}.$\\
By Definition \ref{def_cardinality}, $R^{\dataobs}_r$ is this set.\\
$\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{z \in R^{\dataobs}_r} $.\\
By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R^{\dataobs}_r}  =\sum\limits_{r'\in R^{\dataobs}_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
Apply Lemma \ref{lem_score_pro_eq} in $R^{\dataobs}_r$, \\
$\implies$ for any $r', r''\in R^{\dataobs}_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
$\implies$ $\sum\limits_{r'\in R^{\dataobs}_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
$\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
\end{proof}

@@

Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. In Beta-binomial system, for any $r\in \candidateset$, let $\epsilon\geq 0$ and $\ux{r} + k \geq 0$, the following \emph{sliding property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}.
\end{equation*}
\end{lem}

@@

\todo{
In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$. Let $\mathcal{R}_1$, $\mathcal{R}_2$ be a partition of $\candidateset$:
\begin{itemize}
  \item[*] $\mathcal{R}_1 = \{r | r \in \candidateset\ s.t.\ \cardinality{\dataobs}{r} = 1\}$.
  \item[*] $\mathcal{R}_2 = \{r | r \in \candidateset\ s.t.\ \cardinality{\dataobs}{r} = 2\}$.
\end{itemize}
}

@@

\noindent \textbf{Dilation Property of $\hexpmech$}
\begin{lem}
\label{lem_dilation}
Given $\hexpmech(\dataobs)$ in Beta-binomial system, for any $r\in \candidateset$, let $\lambda < |\gamma|$, $\epsilon$, $|\delta'| < 1$ and $\gamma \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the following \emph{dilation property} holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}
\leq
e^{\frac{\epsilon}{2}} \hexpmechPr{\dataobs}{\ux{z} = e^{\lambda} \ux{r}} + \frac{\delta'}{2}.
\end{equation*}
\end{lem}

@@

  \begin{assert}
  \label{cardinality_eq}
  For any $r\in \candidateset$, $\cardinality{\dataobs}{r} = \cardinality{\dataobs}{t}$.
  \end{assert}

@@

          Based on the accuracy property of exponential mechanism:
          \begin{equation*}
          \begin{split}
          Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
          & \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},\\
          \end{split}
          \end{equation*}
          we derived the accuracy bound for $\hexpmech$:
          \begin{equation*}
          Pr[u(\hexpmech(\dataobs), \dataobs) \leq c] \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
          \end{equation*}

          apply this bound to Equation. \ref{eq_dilation_case2}:
          \begin{equation*}
          \begin{split}
          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
          & = |\candidateset|exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
          & = |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
          \end{split}
          \end{equation*}

          By setting $|\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}) = 1 - \frac{\delta'}{2}$, 
          \begin{equation*}
          \begin{split}
          Pr[\ux{r} \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] = 1 - \frac{\delta'}{2}
          \end{split}
          \end{equation*}
          holds, i.e.,
          \begin{equation*}
          \ux{r}
          \leq 
          \frac{S(\dataobs)}{(1 - e ^ {\lambda})},
          \end{equation*}         
          holds with failure probability $\frac{\delta'}{2}$ is proved.

          Particularly, $|\candidateset| = n + 1$ because in Beta-binomial system.

@@

      Apply Lemma \ref{lem_dilation}:
      \begin{equation*}
      \begin{split}
      & \leq \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \hexpmechPr{\dataobs}{\ux{z} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r} } \\
      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big).
      \end{split}
      \end{equation*}

      Let $\ux{t} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r}$:      
      \begin{equation*}
      \begin{split}
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \hexpmechPr{\dataobs}{\ux{z} = \ux{t} } \\
      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big).
      \end{split}
      \end{equation*}

      Apply Lemma \ref{lem_score_pro_convert}:
      \begin{equation*}
      \begin{split}
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \cardinality{\dataobs}{t} \cdot \hexpmechPr{\dataobs}{z = t } \\
      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big).
      \end{split}
      \end{equation*}

      Apply Definition \ref{def_smoo} and $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$:
      \begin{equation*}
      \begin{split}          
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \cardinality{\dataobs}{t}  \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big).
      \end{split}
      \end{equation*}

      Apply $\ux{t} = \frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}) \uxadj{r}$ and simplify:\\
      \begin{equation*}
      \begin{split}          
      & = \frac{1}{\cardinality{\dataobs}{r}} \Big( e^{(\frac{\epsilon (\uxadj{r} - \ux{r})}{2 S(\dataobs)} + \ln 2)} 
      \big( e^{\frac{\epsilon}{2}}
      \cardinality{\dataobs}{t} \frac{exp(\frac{-\epsilon (\uxadj{r})}{2 S(\dataobs')})}{\unomalizer{\dataobs'}}\\
      & + 1 - |\candidateset|exp(\frac{\epsilon}{2 (1 - e ^ {\ln(\frac{S(\dataobs)}{S(\dataobs')} \ln(\frac{NL(\dataobs)}{NL(\dataobs')}))})}) 
      \big ) \Big).
       \end{split}
      \end{equation*}
